Informing policy via dynamic models: Cholera in Haiti

### 2024-04-03 ms.Rnw
removed cache=TRUE
Removed middle initial from Anna's name, per her request

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Informing policy via dynamic models: Cholera in Haiti} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Jesse Wheeler\textsuperscript{1*},
AnnaElaine L. Rosengart\textsuperscript{2},
Zhuoxun Jiang\textsuperscript{1},
Kevin Tan\textsuperscript{3},
Noah Treutle\textsuperscript{1},
Edward L. Ionides\textsuperscript{1}
\\
\bigskip
\textbf{1} Statistics Department, University of Michigan, Ann Arbor, Michigan, USA
\\
\textbf{2} Statistics and Data Science, Carnegie Mellon University, Pittsburgh, Pennsylvania, USA
\\
\textbf{3} Wharton Statistics and Data Science, University of Pennsylvania, Philadelphia, Pennsylvania, USA
\\
\bigskip

@@

<<Calculate Bench Likelihood, echo=FALSE, message=FALSE, include=FALSE, cache=TRUE>>=

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Informing policy via dynamic models: Cholera in Haiti} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Jesse Wheeler\textsuperscript{1*},
AnnaElaine Rosengart\textsuperscript{2},
Zhuoxun Jiang\textsuperscript{1},
Kevin Tan\textsuperscript{3},
Noah Treutle\textsuperscript{1},
Edward L. Ionides\textsuperscript{1}
\\
\bigskip
\textbf{1} Statistics Department, University of Michigan, Ann Arbor, Michigan, USA
\\
\textbf{2} Statistics and Data Science, Carnegie Mellon University, Pittsburgh, Pennsylvania, USA
\\
\textbf{3} Wharton Statistics and Data Science, University of Pennsylvania, Philadelphia, Pennsylvania, USA
\\
\bigskip

@@

<<Calculate Bench Likelihood, echo=FALSE, message=FALSE, include=FALSE, cache=FALSE>>=
